Defending Against Web Application Attacks: Approaches, Challenges and Implications \vspace{-1mm}

### 2016-09-19 docs/paper/questioning.tex
updated the paper based on Panos' comments

\hlc[yellow]{A recent attack called {\sc php} Object Injection
({\sc poi})}~\cite{DKH14} \hlc[yellow]{does not directly involve
the injection of code, but still achieves arbitrary code execution
in the context of a {\sc php} application through the
injection of specially crafted objects
(e.g. as part of cookies).
When deserialized
by the application, these objects result in
arbitrary code execution.}
Note that the exploitation model we propose
in the following Section also captures such attacks.

@@

An attacker can initiate an injection attack through two main routes.
One way is to use the browser of a victim as an attack
vehicle, through which the code will be injected in the application.
For example, the attacker could embed a malicious script into a {\sc
  url} and then trick a user to click on it through social
engineering, e.g., by sending a phishing email (transition {\sc p-xss} 1.1, {\sc
  n-xss} 1.1, {\sc csrf} 1). Alternatively, the attacker may be able
to inject directly the malicious code on the server through an {\sc http} request
({\sc dsl} 1, {\sc p-xss} 1, {\sc n-xss} 1, {\sc i-csrf} 1). This would happen
in a web application that accepts and processes user input
without appropriate validation. An attacker could upload data
containing a specially crafted script
to steal the cookies of the visiting users ({\sc p-xss} 1, {\sc n-xss} 1),
an {\tt img} tag including a malicious {\sc http} request ({\sc csrf 1}, {\sc
i-csrf 1}),
or embed malicious
{\sc sql} code to retrieve private data from a database ({\sc dsl} 1).
Note that, {\sc xss} and {\sc csrf} attacks can start from both routes.
Once the injected code reaches the vulnerable application, it becomes
a part of a value represented by a program variable. The target of the
attack determines the route from that point and on. In an {\sc sql} injection
attack, the injected code becomes part of a query that
eventually reaches the database where it is executed.

Cross-site scripting
attacks fall into \hlc[yellow]{three} categories,
{\it non-persistent}
(also known as \emph{reflected}) {\sc xss},
{\it persistent} (also known as \emph{stored}) {\sc xss}
\hlc[yellow]{and {\sc dom}\textit{-based} \textsc{xss}.}
Non-persistent {\sc xss} attacks take place when the
data provided by a user is processed on-the-fly
by server-side application logic and ends up without proper sanitization
into a dynamically generated response ({\sc p-xss} 7, {\sc n-xss} 2)
that is eventually rendered by the user's browser.
Thus, in a non-persistent {\sc xss} attack, the injected code
is not saved on the server, but immediately becomes part of the
content that is sent back to a user.
In persistent {\sc xss} attacks, on the other hand,
malicious code is permanently stored on the server ({\sc p-xss} 5).
The injected code residing at server-side then re-enters the
application's execution flow and becomes part of the content that is
eventually sent to the user as part of a future response.
\hlc[yellow]{In a {\sc dom}-based {\sc xss} attack,
the malicious payload is executed as a result of
the modification of the {\sc dom}
environment so that the client-side code runs
in an unanticipated manner,
even if the {\sc http} response that
triggers the injection seems legitimate.
Notably,
a {\sc dom}-based {\sc xss} attack
can follow the path of either a persistent {\sc xss}
attack or a non-persistent {\sc xss} attack.
Also,
it can be performed on-demand and purely client-side
across frames.}

\hlc[yellow]{A Cross Frame Scripting (\textsc{xfs})
attack is a recent threat that combines
a malicious script with
an {\tt iframe} that loads a legitimate page in
an effort to steal data from a user.
Consider an attacker that lures
a user to navigate to a web page the attacker controls
via social engineering.
The attacker's page then loads JavaScript
and an {\sc html} {\tt iframe} pointing to a legitimate site.
Once the user enters his or her
credentials into the legitimate site,
the malicious script records all keystrokes.
An {\sc xfs} attack can be captured by our model
because the steps needed are pretty similar to the steps of
a non-persistent \textsc{xss} attack.}

@@

Web application defenses 
crucially have to capture the presence of an attack. This, however, does not
make a defense mechanism immediately useful. A
detection mechanism must also be reliable.
Detection accuracy is gauged with the following
metrics~\cite{GFDLS06,A00}:
\vspace{-0.7mm}
\begin{itemize}
\item {\bf Sensitivity}: the probability that an attack will be
  caught.
\item {\bf Specificity}: the probability that a normal interaction
  will not be flagged.
\item {\bf Positive Predictive Value} ({\sc ppv}): the probability that a
  reported attack is a real attack. It is the conditional probability
  that an event is an attack if the detection mechanism flags it as
  such. 
\item {\bf Negative Predictive Value} ({\sc npv}): the probability that if
  nothing is reported, no attack has taken place. It is the conditional
  probability that an event is not an attack given that the detection
  mechanism flags it as normal.
\end{itemize}
\vspace{-0.7mm}
\noindent
We will focus on sensitivity and specificity; we will come back to
\textsc{ppv} and \textsc{npv} in Section~\ref{sec:lessons-learned}.
Sensitivity and specifity are defined as follows~\cite{linn2004}:
\vspace{-0.7mm}
\begin{itemize}
\item True Positive (\textsc{tp}): an attack that raises an alarm.
\item True Negative (\textsc{tn}): an event that is not an attack and that does
  not raise an alarm.
\item False Positive (\textsc{fp}): an event that although it is not an attack,
  raises an alarm.
\item False Negative (\textsc{fn}): an event that although is an attack, does
  not raise an alarm.
\end{itemize}
\vspace{-0.7mm}
\noindent
With these we can calculate:

@@

To ensure reproducibility of research results, the source code
implementing a detection mechanism should be available to researchers.
Ideally the code should be available under an open source license, so
that it is easy to modify and improve an approach; even when this is
not possible, for whatever reason, it is important to make sure that
all computer code and test data is available, noting any restrictions
on accessibility. Availability of computer code has been recognized as
an important issue outside the computer science field: the journal
\emph{Nature}, in a recent editorial, adopted a publication policy stressing
access to code and data~\cite{nature2014}. At a time and date that the
merits of open access to code are discussed in non computer science
journals~\cite{easterbrook2014}, we should expect computer scientists
to lead the way.

@@

We categorize and analyze a large set of defenses developed to prevent
the attacks described in Sections~\ref{sec:attacks} and~\ref{sec:model}.
We perform our analysis across
the dimensions discussed in the previous section,
except from availability, which we treat
separately in Section~\ref{sec:discussion}.
Due to the immense number of published works in the area, we only consider
defenses that have been proposed in publications cited more than
20 times according to Google Scholar.
We also include some recent works that have been
presented in top security conferences, even though they have been
cited less than twenty times, so that recent research is not penalized.

@@

\vspace{-1mm}
Some frameworks define policies based on information and
features provided by the Document Object Model ({\sc dom}) of a web
page. Specifically, developers must place all legitimate scripts
inside {\sc html} elements like {\tt div}. The web browser (Point {\sc
  ub}) parses the {\sc dom} tree and executes scripts only when they
are contained in such elements. All other scripts are treated
according to the policies defined on the server. Frameworks that
support this functionality include {\sc beep}~\cite{TNH07} and {\sc
  dsi}~\cite{NSS06}. The main problem with these mechanisms is that
they do not examine the script's location inside the web document.
Attackers can take advantage of this fact to perform mimicry attacks~\cite{WS02}.
Specifically, they can execute legitimate scripts, but not as intended
by the original design of the developers. This is extensively
described by Athanasopoulos et al.~\cite{APKLM10}, who also describe
another recent variation of JavaScript injection attacks, known as
return-to-JavaScript attacks, which can be used to bypass the above
mechanisms.

\vspace{-1.5mm}
A policy enforcement technique developed by Mozilla,
called {\sc csp} (Content Security
Policy)\footnote{\scriptsize\url{https://developer.mozilla.org/en-US/docs/Web/Security/CSP}}~\cite{SSM10}
is currently supported by many browsers to prevent
{\sc xss} and {\sc csrf} attacks. To eliminate such
attacks, web site administrators
can specify which domains the browser should treat
as valid sources of script and which not.
\hlc[yellow]{These policies are communicated via the {\sc http} header.}
Then, the browser
(Point {\sc ub}) will only execute scripts that exist in
source files from white-listed domains.
Note that,
if an application involves
embedded scripts, developers must utilize
the {\sc csp}'s {\em nonce} concept.
This is an unpredictable,
random value indicated in
the {\tt script-src} directive which in turn,
is applied as a nonce attribute to
{\tt <script>} elements.
As a result, only those elements that have the
correct nonce will execute.
Even if an attacker
is able to inject markup into the page,
the attack will be prevented by the attacker's
inability to guess the nonce value.
However, attackers may still bypass this feature
and invoke a script from a non-whitelisted source.
To do so, their injected code must
be crafted in a way that the nonce is handled
by the browser as an attribute of the payload~\cite{jigsaw}.

@@

{\sc isr} is a method that has been applied to counter different kinds
of application attacks~\cite{K09b}, and was originally applied for the
prevention of binary code injection attacks~\cite{KKP03}.
The main idea behind {\sc isr} is
to change the representation of code
based on a randomly chosen transformation,
and randomizing the execution environment accordingly.
In this way, any malicious code injected as part of untrusted input data,
by attackers who do not know the randomization algorithm,
will not be executed.

@@

An issue that involves all taint tracking schemes involves
the difficulty of maintaining accurate taints~\cite{GMPS11}
(e.g. implicit flows~\cite{ME07}).
In such cases, certain, tainted inputs can escape the tracking mechanism.
Keeping track of such input \hlc[yellow]{may be} impractical not only because of the
various technical difficulties, but also because it would raise false alarms.

@@

In general, the detection accuracy of training approaches is heavily
influenced by the coverage that is achieved during the training phase. If
the coverage is insufficient false alarms are very likely. In
addition, when a code statement is altered, a new training phase is
necessary.

@@

\hlc[yellow]{Information Flow Control ({\sc ifc})
mechanisms combine positive taint tracking and
policy enforcement to prevent {\sc xss} attacks on the
client-side (Point {\sc ub}).
Representative implementations such as
{\sc jsf}low}~\cite{HBBS14}\hlc[yellow]{, {\sc cowl}}~\cite{SYMRHKM14}
\hlc[yellow]{and the framework by Bauer et al.}~\cite{BCJPST15}
\hlc[yellow]{allow developers to express information flow
policies be extending the type system of JavaScript.
Then,
the policies are enforced by the JavaScript interpreter
through dynamic checks.}
\hlc[yellow]{{\sc ifc} frameworks do not
focus explicitly on JavaScript and they
have a broader scope.
They can be used to build secure applications,
thus preventing different attacks.
Policies can be provided either as compile-time
program annotations,
or as run-time requirements defined by the user.
Such frameworks include {\sc sif}
(Servlet Information Flow)}~\cite{CVMA07}\hlc[yellow]{,
% Ur/Web}~\cite{C10b}\hlc[yellow]{,
Hails}~\cite{GLSTMMR12}
\hlc[yellow]{, and Aeolus}~\cite{CPSPBCCSL12}.

@@

Regarding the subjects of tests,
we see that \hlc[yellow]{30} out of \hlc[yellow]{41 (73.1\%)}
mechanisms were tested with real-world
applications known to be vulnerable.
The vulnerabilities associated with these applications
are enlisted in the following providers: the Common
Vulnerabilities and Exposures ({\sc cve})
database,\footnote{\scriptsize\url{https://cve.mitre.org/}}
%~\cite{cve},
the Bugtraq\footnote{\scriptsize\url{http://seclists.org/bugtraq/}}
security mailing list,
%~\cite{bugtraq},
the {\sc xss}ed.com
security bulletin provider,\footnote{\scriptsize\url{www.xssed.com}}
%~\cite{xssed},
Microsoft's security
bulletin\footnote{\scriptsize\url{https://technet.microsoft.com/en-us/security/bulletin}}
%~\cite{microsoftBulletin}
and the
ha.ckers.org\footnote{\scriptsize\url{http://ha.ckers.org/}}
security bulletin provider.
%~\cite{hackers}.
Figure~\ref{fig:defect_sources},
presents how many,
and which, in the figure's caption, publications referred
to which source.
In numerous occasions authors performed tests based
on the same applications.
For example, 12 mechanisms were tested on a
vulnerable version of the {\sc phpbb} bulletin board
software.\footnote{\scriptsize\url{https://www.phpbb.com/}}
%~\cite{phpbb}.

@@

\subsection{Availability}
\vspace{-0.8mm}

@@

Table~\ref{tab:avail} presents our findings regarding the availability
of each mechanism in terms of source code and corresponding
executables. We also examined the availability of the testbeds
mentioned in each paper. We see that only \hlc[yellow]{8} out of \hlc[yellow]{41 (19.5\%)} of the
publications provided a link to their mechanism and, 2 from these 6
web pages are currently not available. In \hlc[yellow]{7} cases authors made either
the source code or their executables available after their paper got
published. In one case ({\sc csp}~\cite{SSM10}), the source was available before the
publication through the Mozilla community.
Regarding the availability of test materials, we see that
only \hlc[yellow]{4} out of \hlc[yellow]{41 (9.7\%)} publications have currently their testbeds
available.

@@

Table~\ref{tab:comp} shows the performance overhead of each mechanism.
In addition, it indicates if the overhead is incurred at the
server ({\sc s}) or at the client-side ({\sc c}). In almost half of
the approaches, \hlc[yellow]{20} out of \hlc[yellow]{41 (48.7\%)}, the overhead is provided as a
percentage, while in other cases, \hlc[yellow]{8} our of \hlc[yellow]{41 (19.5\%)}, the authors
provide the latency (in ms) that their mechanisms add to the
normal execution time of the protected application. Note that in some
cases, the times of normal executions are not provided,
so it is not possible to convert absolute
time measurements to percentage overheads. In 10 cases (\hlc[yellow]{24.3\%}), the
overhead was either not available ({\sc na})
or not quantified ({\sc nq}).
\hlc[yellow]{For \textsc{php} Aspis}~\cite{PMP11}
\hlc[yellow]{and {\sc jsf}low}~\cite{HBBS14}
\hlc[yellow]{, the authors indicate that with
their mechanisms, the execution time is doubled.}

@@

\hlc[yellow]{A reasonable argument would be that many mechanisms
(e.g. many mechanisms coming from the etiological category,
or the {\sc ifc} frameworks), do not need to be
established purely through testing, since they provide systematic
arguments as to why their design is secure against attacks.
In order for this to hold,
however, their implementation should be flawless
and precisely follow its specification, which may not
be the case in practice. Moreover, even mechanisms that detect attacks
based on their root cause, instead of their observed behavior, may still be
circumvented by evasive attacks.}

@@

\hlc[yellow]{From a security perspective,
we saw that there are cases where
mechanisms coming from the same category
can be bypassed by similar attack patterns.
This denotes that there are issues
found in the design of each approach.
Recall for instance,
that implicit flows can be used against
many taint tracking solutions,
and mimicry attacks can be launched
to bypass training and policy enforcement defenses.
{\sc ifc} mechanisms though,
can deal with such attacks.
This indicates that when solutions
borrow elements from other categories
(recall that {\sc ifc} mechanisms
belong to the hybrid category)
could be more effective.
Also,
we could say that different mechanisms could
be used together to defend different attacks.
For instance,
developers could employ both {\sc csp}}~\cite{SSM10}
\hlc[yellow]{and \textsc{sql}rand}~\cite{BK04}
\hlc[yellow]{to deal with {\sc xss}
and {\sc sql} injection respectively.}

@@

To the positive side, some defenses have been extensively tested in
terms of accuracy ({\sc sqlc}heck~\cite{SW06},
{\sc amnesia}~\cite{HO05b}, libAnomaly~\cite{VMV05}),
solve specific problems in an effective way
(Blueprint~\cite{LV09} and the system by Stock et al.~\cite{SLMS14}) or
have a low computational overhead
({\sc dsi}~\cite{NSS06} and the system by Phung et al.~\cite{PSC09}).
There are also cases where
researchers have made their code available ({\sc beep}~\cite{TNH07}
and {\sc sd}river~\cite{MS09}),
which can promote the development of better
mechanisms. This argument has been raised by others
researchers too~\cite{SPWS13}.
Furthermore, testing defenses in a production
setting could also propel their adoption.

@@

\vspace{-3mm}

>>>>

\hlc[yellow]{A recent attack called {\sc php} Object Injection
({\sc poi})}~\cite{DKH14} \hlc[yellow]{does not directly involve
the injection of code, but still achieves arbitrary code execution
in the context of a {\sc php} application through the
injection of specially crafted objects
(e.g., as part of cookies).
When deserialized
by the application, these objects result in
arbitrary code execution.}
Note that the exploitation model we propose
in the following Section also captures such attacks.

@@

An attacker can initiate an injection attack through two main routes.
One way is to use the browser of a victim as an attack
vehicle, through which the code will be injected in the application.
For example, the attacker could embed a malicious script into a {\sc
  url} and then trick a user to click on it through social
engineering, e.g., by sending a phishing email (transition {\sc p-xss} 1.1, {\sc
  n-xss} 1.1, {\sc csrf} 1). Alternatively, the attacker may be able
to inject directly the malicious code on the server through an {\sc http} request
({\sc dsl} 1, {\sc p-xss} 1, {\sc n-xss} 1, {\sc i-csrf} 1). This would happen
in a web application that accepts and processes user input
without appropriate validation. An attacker could upload data
containing a specially crafted script
to steal the cookies of the visiting users ({\sc p-xss} 1, {\sc n-xss} 1),
an {\tt img} tag including a malicious {\sc http} request ({\sc csrf 1}, {\sc
i-csrf 1}),
or embed malicious
{\sc sql} code to retrieve private data from a database ({\sc dsl} 1).
Note that {\sc xss} and {\sc csrf} attacks can start from both routes.
Once the injected code reaches the vulnerable application, it becomes
a part of a value represented by a program variable. The target of the
attack determines the route from that point and on. In an {\sc sql} injection
attack, the injected code becomes part of a query that
eventually reaches the database where it is executed.

Cross-site scripting
attacks fall into \hlc[yellow]{three} categories,
{\it non-persistent}
(also known as \emph{reflected}) {\sc xss},
{\it persistent} (also known as \emph{stored}) {\sc xss}
\hlc[yellow]{and \textit{Document Object Model} ({\sc dom})
\textit{-based} \textsc{xss}.}
Non-persistent {\sc xss} attacks take place when the
data provided by a user is processed on-the-fly
by server-side application logic and ends up without proper sanitization
into a dynamically generated response ({\sc p-xss} 7, {\sc n-xss} 2)
that is eventually rendered by the user's browser.
Thus, in a non-persistent {\sc xss} attack, the injected code
is not saved on the server, but immediately becomes part of the
content that is sent back to a user.
In persistent {\sc xss} attacks, on the other hand,
malicious code is permanently stored on the server ({\sc p-xss} 5).
The injected code residing at server-side then re-enters the
application's execution flow and becomes part of the content that is
eventually sent to the user as part of a future response.
\hlc[yellow]{{\sc dom}-based {\sc xss} attacks involve
the modification of the {\sc dom} of a webpage.
The {\sc dom} treats an {\sc html} document
as a tree structure where each node is an
object representing a part of the document.
Each object can be accessed and manipulated
programmatically and any visible changes
may then be reflected in the browser.
In a {\sc dom}-based {\sc xss} attack,
the malicious payload
(e.g., hidden in a well-crafted {\sc url}
that is sent to a user via phishing:
\textsc{n-xss} 1.1)
is executed as a result of
the manipulation of the {\sc dom}
environment
(e.g., when another flawed script accesses the
modified {\sc dom} object)
and is not contained in
the {\sc http} response.
That is,
the malicious payload never reaches the server.
Such an attack can be performed
purely client-side across {\sc html} frames.
Hence,
server-side defenses might not be effective
in this case.}

\hlc[yellow]{A Cross Frame Scripting (\textsc{xfs})
attack is a recent threat that combines
a malicious script with
an {\tt iframe} that loads a legitimate page in
an effort to steal data from a user.
Consider an attacker that lures via social engineering
a user to navigate to a web page the attacker controls.
The attacker's page then loads JavaScript
and an {\sc html} {\tt iframe} pointing to a legitimate site.
Once the user enters his or her
credentials into the legitimate site,
the malicious script records all keystrokes.}

@@

Web application defenses 
crucially have to capture the presence of an attack. This, however, does not
make a defense mechanism immediately useful. A
detection mechanism must also be reliable.
Detection accuracy is gauged with the following
metrics~\cite{GFDLS06,A00}:
\vspace{-0.7mm}
\begin{itemize}
\item {\bf Sensitivity}: the probability that an attack will be
  caught.
\item {\bf Specificity}: the probability that a normal interaction
  will not be flagged.
\item {\bf Positive Predictive Value} ({\sc ppv}): the probability that a
  reported attack is a real attack. It is the conditional probability
  that an event is an attack if the detection mechanism flags it as
  such. 
\item {\bf Negative Predictive Value} ({\sc npv}): the probability that if
  nothing is reported, no attack has taken place. It is the conditional
  probability that an event is not an attack given that the detection
  mechanism flags it as normal.
\end{itemize}
\vspace{-0.7mm}
\noindent
We will focus on sensitivity and specificity; we will come back to
\textsc{ppv} and \textsc{npv} in Section~\ref{sec:lessons-learned}.
Sensitivity and specifity are defined using the following~\cite{linn2004}:
\vspace{-0.7mm}
\begin{itemize}
\item True Positive (\textsc{tp}): an attack that raises an alarm.
\item True Negative (\textsc{tn}): an event that is not an attack and that does
  not raise an alarm.
\item False Positive (\textsc{fp}): an event that although it is not an attack,
  raises an alarm.
\item False Negative (\textsc{fn}): an event that although is an attack, does
  not raise an alarm.
\end{itemize}
\vspace{-0.7mm}
\noindent
So that we can calculate:

@@

To ensure reproducibility of research results, the source code
implementing a detection mechanism should be available to researchers.
Ideally the code should be available under an open source license, so
that it is easy to modify and improve an approach; even when this is
not possible, for whatever reason, it is important to make sure that
all computer code and test data is available, noting any restrictions
on accessibility. Availability of computer code has been recognized as
an important issue outside the computer science field: the journal
\emph{Nature} has adopted a publication policy stressing
access to code and data~\cite{nature2014}. At a time and date that the
merits of open access to code are discussed in non computer science
journals~\cite{easterbrook2014}, we should expect computer scientists
to lead the way.

@@

We categorize and analyze a large set of defenses developed to prevent
the attacks described in Sections~\ref{sec:attacks} and~\ref{sec:model}.
We perform our analysis across
the dimensions discussed in the previous section,
except from availability, which we treat
separately in Section~\ref{sec:discussion}.
Due to the immense number of published works in the area, we only consider
defenses that have been proposed in publications cited more than
20 times according to Google Scholar.
We also include some recent works that have been
presented in top security conferences, even though they have been
cited less than 20 times, so that recent research is not penalized.

@@

\vspace{-1mm}
Some frameworks define policies based on information and
features provided by the {\sc dom} of a web
page. Specifically, developers must place all legitimate scripts
inside {\sc html} elements like {\tt div}. The web browser (Point {\sc
  ub}) parses the {\sc dom} tree and executes scripts only when they
are contained in such elements. All other scripts are treated
according to the policies defined on the server. Frameworks that
support this functionality include {\sc beep}~\cite{TNH07} and {\sc
  dsi}~\cite{NSS06}. The main problem with these mechanisms is that
they do not examine the script's location inside the web document.
Attackers can take advantage of this fact to perform mimicry attacks~\cite{WS02}.
Specifically, they can execute legitimate scripts, but not as intended
by the original design of the developers. This is extensively
described by Athanasopoulos et al.~\cite{APKLM10}, who also describe
another recent variation of JavaScript injection attacks, known as
return-to-JavaScript attacks, which can be used to bypass the above
mechanisms.

\vspace{-1.5mm}
A policy enforcement technique developed by Mozilla,
called {\sc csp} (Content Security
Policy)\footnote{\scriptsize\url{https://developer.mozilla.org/en-US/docs/Web/Security/CSP}}~\cite{SSM10}
is currently supported by many browsers to prevent
{\sc xss} and {\sc csrf} attacks. To eliminate such
attacks, web site administrators
can specify which domains the browser should treat
as valid sources of script and which not.
\hlc[yellow]{These policies are communicated via the {\sc http} headers.}
Then, the browser
(Point {\sc ub}) will only execute scripts that exist in
source files from white-listed domains.
Note that,
if an application involves
embedded scripts, developers must utilize
the {\sc csp}'s {\em nonce} concept.
This is an unpredictable,
random value indicated in
the {\tt script-src} directive,
which in turn is applied as a nonce attribute to
{\tt <script>} elements.
As a result, only those elements that have the
correct nonce will execute.
Even if an attacker
is able to inject markup into the page,
the attack will be prevented by the attacker's
inability to guess the nonce value.
However, attackers may still bypass this feature
and invoke a script from a non-whitelisted source.
To do so, their injected code must
be crafted in a way that the nonce is handled
by the browser as an attribute of the payload~\cite{jigsaw}.

@@

{\sc isr} is a method that has been applied to counter different kinds
of application attacks~\cite{K09b}, and was originally applied for the
prevention of binary code injection attacks~\cite{KKP03}.
The main idea behind {\sc isr} is
to change the representation of code
based on a randomly chosen transformation,
and randomize the execution environment accordingly.
In this way, any malicious code injected as part of untrusted input data,
by attackers who do not know the randomization algorithm,
will not be executed.

@@

An issue that involves all taint tracking schemes involves
the difficulty of maintaining accurate taints~\cite{GMPS11}
(e.g., implicit flows~\cite{ME07}).
In such cases, certain, tainted inputs can escape the tracking mechanism.
Keeping track of such input \hlc[yellow]{may be} impractical not only because of the
various technical difficulties, but also because it would raise false alarms.

@@

In general, the detection accuracy of training approaches is heavily
influenced by the coverage that is achieved during the training phase. If
the coverage is insufficient,
false alarms are very likely. In
addition, when a code statement is altered, a new training phase is
necessary.

@@

\hlc[yellow]{Information Flow Control ({\sc ifc})
mechanisms combine positive taint tracking and
policy enforcement to prevent {\sc xss} attacks on the
client-side (Point {\sc ub}).
Representative implementations such as
{\sc jsf}low}~\cite{HBBS14}\hlc[yellow]{, {\sc cowl}}~\cite{SYMRHKM14}
\hlc[yellow]{and the framework by Bauer et al.}~\cite{BCJPST15}
\hlc[yellow]{allow developers to express information flow
policies extending the type system of JavaScript.
Then,
the policies are enforced by the JavaScript interpreter
through dynamic checks.}
\hlc[yellow]{{\sc ifc} frameworks do not
focus explicitly on JavaScript and they
have a broader scope.
They can be used to build secure applications,
thus preventing different attacks.
Policies can be provided either as compile-time
program annotations,
or as run-time requirements defined by the user.
Such frameworks include {\sc sif}
(Servlet Information Flow)}~\cite{CVMA07}\hlc[yellow]{,
% Ur/Web}~\cite{C10b}\hlc[yellow]{,
Hails}~\cite{GLSTMMR12}
\hlc[yellow]{, and Aeolus}~\cite{CPSPBCCSL12}.

@@

Regarding the subjects of tests,
we see that \hlc[yellow]{30} out of \hlc[yellow]{41 (73.1\%)}
mechanisms were tested with real-world
applications known to be vulnerable.
The vulnerabilities associated with these applications
are enlisted in the following providers: the Common
Vulnerabilities and Exposures ({\sc cve})
database,\footnote{\scriptsize\url{https://cve.mitre.org/}}
%~\cite{cve},
the Bugtraq\footnote{\scriptsize\url{http://seclists.org/bugtraq/}}
security mailing list,
%~\cite{bugtraq},
the {\sc xss}ed.com
security bulletin provider,\footnote{\scriptsize\url{www.xssed.com}}
%~\cite{xssed},
Microsoft's security
bulletin\footnote{\scriptsize\url{https://technet.microsoft.com/en-us/security/bulletin}}
%~\cite{microsoftBulletin}
and the
ha.ckers.org\footnote{\scriptsize\url{http://ha.ckers.org/}}
security bulletin provider.
%~\cite{hackers}.
Figure~\ref{fig:defect_sources}
presents how many,
and which publications referred
to which source.
In numerous occasions authors performed tests based
on the same applications.
For example, 12 mechanisms were tested on a
vulnerable version of the {\sc phpbb} bulletin board
software.\footnote{\scriptsize\url{https://www.phpbb.com/}}
%~\cite{phpbb}.

@@

\vspace{-0.5mm}
\subsection{Availability}
\vspace{-0.8mm}

@@

Table~\ref{tab:avail} presents our findings regarding the availability
of each mechanism in terms of source code and corresponding
executables. We also examined the availability of the testbeds
mentioned in each paper. We see that only \hlc[yellow]{8} out of \hlc[yellow]{41 (19.5\%)} of the
publications provided a link to their mechanism and, 2 from these 6
web pages are currently not available.
In \hlc[yellow]{7} cases the authors made either
the source code or their executables available after their paper got
published. In one case ({\sc csp}~\cite{SSM10}), the source was available before the
publication through the Mozilla community.
Regarding the availability of test materials, we see that
only \hlc[yellow]{4} out of \hlc[yellow]{41 (9.7\%)} publications have currently their testbeds
available.

@@

Table~\ref{tab:comp} shows the performance overhead of each mechanism.
In addition, it indicates if the overhead is incurred at the
server ({\sc s}) or at the client-side ({\sc c}). In almost half of
the approaches, \hlc[yellow]{20} out of \hlc[yellow]{41 (48.7\%)}, the overhead is provided as a
percentage, while in other cases, \hlc[yellow]{8} our of \hlc[yellow]{41 (19.5\%)}, the authors
provide the latency (in ms) that their mechanisms add to the
normal execution time of the protected application.
Note that in some
cases, the times of normal executions are not provided
so it is not possible to convert absolute
time measurements to percentage overheads. In 10 cases (\hlc[yellow]{24.3\%}), the
overhead was either not available ({\sc na})
or not quantified ({\sc nq}).
\hlc[yellow]{For \textsc{php} Aspis}~\cite{PMP11}
\hlc[yellow]{and {\sc jsf}low}~\cite{HBBS14}
\hlc[yellow]{the authors indicate that with
their mechanisms the execution time is doubled.}

@@

\hlc[yellow]{A reasonable argument would be that many defenses
(e.g., many mechanisms coming from the etiological category,
or the {\sc ifc} frameworks), do not need to be
validated purely through testing, since they provide systematic
arguments as to why their design is secure against attacks.
In order for this to hold,
however, their implementation should be flawless
and precisely follow its specification, which may not
be the case in practice. Moreover, even mechanisms that detect attacks
based on their root cause, instead of their observed behavior, may still be
circumvented by evasive attacks.}

@@

\hlc[yellow]{From a security perspective,
we saw that there are cases where
mechanisms coming from the same category
can be bypassed by similar attack patterns.
This denotes that there are issues
found in the design of each approach.
Recall,
for instance,
that implicit flows can be used against
many taint tracking solutions,
and mimicry attacks can be launched
to bypass training and policy enforcement defenses.
{\sc ifc} mechanisms though,
can deal with such attacks.
This indicates that when solutions
borrow elements from other categories
({\sc ifc} mechanisms
belong to the hybrid category)
could be more effective.
Also,
we could say that different mechanisms could
be used together to defend different attacks.
For instance,
developers could employ both {\sc csp}}~\cite{SSM10}
\hlc[yellow]{and \textsc{sql}rand}~\cite{BK04}
\hlc[yellow]{to deal with {\sc xss}
and {\sc sql} injection respectively.}

@@

On the positive side, some defenses have been extensively tested in
terms of accuracy ({\sc sqlc}heck~\cite{SW06},
{\sc amnesia}~\cite{HO05b}, libAnomaly~\cite{VMV05}),
solve specific problems in an effective way
(Blueprint~\cite{LV09} and the system by Stock et al.~\cite{SLMS14}),
or have a low computational overhead
({\sc dsi}~\cite{NSS06} and the system by Phung et al.~\cite{PSC09}).
There are also cases where
researchers have made their code available ({\sc beep}~\cite{TNH07}
and {\sc sd}river~\cite{MS09}),
which can promote the development of better
mechanisms. This argument has been raised by others
researchers too~\cite{SPWS13}.
Furthermore, testing defenses in a production
setting could also propel their adoption.

@@
